Numerical Stability of Detonations in White Dwarf Simulations

### 2018-12-02 papers/ignition/paper.tex

% Add discussion about how none of the conclusions depend on the microphysics
% of how ignitions/detonations actually occur -- this paper is simply about
% self-consistent fluid simulations, i.e. are we even correctly solving
% the equations we wrote down, and not focusing on the harder question
% of whether we're solving the right equations.

>>>>

Our example detonation problem demonstrates, at least for this class of
hydrodynamical burning problem, a grid resolution requirement much more stringent
than 1 km. This does not represent all such burning problems: for example, we
have tested similar setups with only carbon and oxygen for which a resolution
in the tens of kilometers is sufficient. However, the fact that it is even
possible for this type of burning to require a resolution better than 100 m
should cast significant uncertainty on the results of simulations featuring
detonations that do not meet this resolution.

This study does not directly address the problem of how, in the detailed
microphysical sense, a detonation wave actually begins to propagate, as
we cannot resolve this length scale even in our highest resolution simulations.
Rather, we are making the point that for simulations in which a macroscopic
detonation wave appears self-consistently, this is only a valid numerical result
if the resolution is sufficiently high. This convergence requirement does
not imply that the detonation itself is physically realistic; but, it does
imply that we are not even correctly solving the fluid equations we intend
to solve when the convergence requirement is not met. We believe that our
test case can be useful in the future for testing algorithmic innovations
that hope to improve the realism of burning at low resolutions.
